---
title: "Two Bayesian inference models: supervised and unsupervised"
# runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This work demonstrates introducing  **latent** variables learning in Bayesian Networks to overcome the common limitations of frequentist (non-Bayesian p-values) statistics and also Bayesian supervised (non-learning) inference 


## Bayesian inference: supervised and unsupervised models

The example shows `data` that has three variables: `converted`, 
`condition` and `hour`. Each website visitor is presented with either `control` or `treatment`  website banner (`condition` variable),  converted and time spent on the website
are also known.

```{r load-packages, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

library(jsonlite)
library(dplyr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(ggpubr)
library(plyr)
#require(RJSONIO) 
library("rwebppl")
```

```{r load data, echo=FALSE}
setwd('~/PycharmProjects/tests/webppl/')

fname = '~/PycharmProjects/tests/webppl/Results2/models_banner_p1_p2.Rdata'
load(fname, verbose = TRUE)

print(str(df_banner))
print(summary(df_banner))
```

## Bayesian inference: supervised and unsupervised models

**Evrything that we don't know has probbaility.**

Infere probability of conversion for 'Control' versus 'Treatment' groups and difference **delta** distribution that can be commonly used for confidence interval.

Modeling based on existing variables 'converted' and 'group' shows no statistical 
signifiance of 'group', confirmed by the frequentist 'p-test'.  

Notuce that variable **time** is continuous and can not be utilized directly for inference.
Oftenly non-learning **rules-based** used, which has multiple problems in production: hard thresholds, doesn't scale, non-learnt rules.


# Model-1: Bayesian Statistical Significance    

Both **p-value** and the convertion probability distributions difference show no evidence of statistical significance for the Control-Treatment condition. 

```{r model-1-plot, echo=FALSE}

p = p_model_1

n2 = length(p[ p["Parameter"]=="control",]$value); n1 = 1; # MCMC: floor(n2/20)

nb1 = 20
b1 = 1/nb1*c(0:nb1)
x = p[ p["Parameter"]=="control",]$value[c(n1:n2)]
y = p[ p["Parameter"]=="treatment",]$value[c(n1:n2)]
z = p[ p["Parameter"]=="delta",]$value[c(n1:n2)]

# h1=hist(x, breaks=b1, main="control", xlab="control", probability = T)
# h2=hist(y, breaks=b1, main="treatment", xlab="treatment", probability = T)
par(mfrow=c(2,1))
  h1=hist(x, breaks = b1, plot=F)
  h2=hist(y, breaks = b1,plot=F)
  plot(h1, col=rgb(1, 0, 0, 0.5), xlim = c(0,1),freq=F,
       xlab = "Converted, Probability", main = "Converted: Control (red) vs. Treatment ")
  plot(h2, col=rgb(0, 1, 0, 0.5),freq=F, xlim = c(0,1), add=TRUE)
  hist(z, breaks=nb1, main="pdf(Control-Treatment): no statistical signifiance", xlab="Control-Treatment", col=rgb(1, 0, 0, 0.5), probability = T)
```

'ggplot'


```{r model-1-plot2, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
require(ggplot2)
require(reshape2)


df_hist <- data.frame(control = p[ p["Parameter"]=="control",]$value[c(n1:n2)],
                      treatment = p[ p["Parameter"]=="treatment",]$value[c(n1:n2)])


ggplot(melt(df_hist), aes(value, fill = variable)) + geom_histogram(position = "dodge",binwidth=0.01) 
```


# Model-2: Robot-Human Latent Variable

Learning a new 'Robot'-'Human' latent variable allows to correrctly identify the significance of the Control-Treatment condition.

```{r model-2-plot1, echo=FALSE}
p = p_model_2

n2 = length(p[ p["Parameter"]=="control",]$value); n1 = floor(n2/20)
par(mfrow=c(2,3))
#b1 = nb1
x = p[ p["Parameter"]=="control",]$value[c(n1:n2)]
y = p[ p["Parameter"]=="treatment",]$value[c(n1:n2)]
z = p[ p["Parameter"]=="delta",]$value[c(n1:n2)]

x1 = p[ p["Parameter"]=="hour_human",]$value[c(n1:n2)]
y1 = p[ p["Parameter"]=="hour_robot",]$value[c(n1:n2)]
z1 = p[ p["Parameter"]=="robot",]$value[c(n1:n2)]

x2 = p[ p["Parameter"]=="hypothesis",]$value[c(n1:n2)]

nb2 = 20
b2 = c(-3:25)
#y = p[ p["Parameter"]=="chooseModel1vsModel2_bernoulli",]$value[c(n1:n2)]
# hist(x, breaks=b1)
# hist(x, breaks=b1, freq=F)
par(mfrow=c(2,2))
  h01=hist(x, breaks = b1, plot=F)
  h02=hist(y, breaks = b1,plot=F)
  h03=hist(z1, breaks = b1,plot=F)
  
  plot(h01, col=rgb(1, 0, 0, 0.5), xlim = c(0,1),freq=F,
       xlab = "Converted, Probability", main = "Converted: Control (red) vs. Treatment (green) vs. Robot ")
  plot(h02, col=rgb(0, 1, 0, 0.5),freq=F, xlim = c(0,1), add=TRUE)
  plot(h03, col=rgb(0, 0, 1, 0.5),freq=F, xlim = c(0,1), add=TRUE)
  
  hist(z, breaks=10, main="pdf Control-Treatment", xlab="Control-Treatment", col=rgb(1, 0, 0, 0.5), probability = T)

  h3=hist(x1, breaks = 10, plot=F)
  h4=hist(y1, breaks = 10,plot=F)
  plot(h3, col=rgb(1, 0, 0, 0.5), xlim = c(0,23),freq=F,
       xlab = "Time", main = "Time: Human (red) vs. Robot ")
  plot(h4, col=rgb(0, 1, 0, 0.5),freq=F, xlim = c(0,23), add=TRUE)
  
  hist(x2, breaks=10, main="pdf hypothesis: Model-2 vs. Model-1)", xlab="Probability, Model-1", 
       xlim=c(0,1), col=rgb(1, 0, 0, 0.5), probability = T)

```


'ggplot'

```{r model-2-plot2, echo=FALSE, message=FALSE}
require(ggplot2)

par(mfrow=c(1,1))
# require(reshape2)
df_hist <- data.frame(human = p[ p["Parameter"]=="hour_human",]$value[c(n1:n2)],
                      robot = p[ p["Parameter"]=="hour_robot",]$value[c(n1:n2)])
ggplot(melt(df_hist), aes(value, fill = variable)) + geom_histogram(position = "dodge",binwidth=1)
```

```{r model-2-plot3, echo=FALSE, message=FALSE}
require(ggplot2)
df_hist <- data.frame(control = p[ p["Parameter"]=="control",]$value[c(n1:n2)],
                      treatment = p[ p["Parameter"]=="treatment",]$value[c(n1:n2)],
                      robot = p[ p["Parameter"]=="robot",]$value[c(n1:n2)])
ggplot(melt(df_hist), aes(value, fill = variable)) + geom_histogram(position = "dodge",binwidth=0.05)
```

# Conclusion: Model-1 vs. Model-2

```{r model-1-plot3, echo=FALSE, message=FALSE}
require(ggplot2)

df_hist <- data.frame("Control minus treatment" = p_model_1[p_model_1["Parameter"]=="delta",]$value,
                      "Human control minus treatment" = p_model_2[ p_model_2["Parameter"]=="delta",]$value)
ggplot(melt(df_hist), aes(value, fill = variable)) + geom_histogram(position = "dodge",binwidth=0.04)
``` 



