---
title: "Two Bayesian inference models: supervised and unsupervised"
# runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This work demonstrates introducing  **latent** variables learning in Bayesian Networks to overcome the common limitations of frequentist (non-Bayesian p-values) statistics and also Bayesian supervised (non-learning) inference 


## Bayesian inference: supervised and unsupervised models

The example shows `data` that has three variables: `converted`, 
`condition` and `hour`. Each website visitor is presented with either `control` or `treatment`  website banner (`condition` variable),  converted and time spent on the website
are also known.

```{r load-packages, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE}

library(jsonlite)
library(dplyr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(ggpubr)
library(plyr)
#require(RJSONIO) 
library("rwebppl")
```

```{r load data, echo=FALSE}
setwd('~/PycharmProjects/tests/webppl/Results2')

# fname = './data_banner.Rdata'
fname = './data_banner_countries.Rdata'

load(fname, verbose = TRUE)

print(str(df_banner))
print(summary(df_banner))

df_countries200 = df_countries[sample(nrow(df_countries), 200), ]

print(str(df_countries200))
print(summary(df_countries200))
```

## Bayesian inference: supervised and unsupervised models

**Evrything that we don't know has probbaility.**

Infere probability of conversion for 'Control' versus 'Treatment' groups and difference **delta** distribution that can be commonly used for confidence interval.

Modeling based on existing variables 'converted' and 'group' shows no statistical 
signifiance of 'group', confirmed by the frequentist 'p-test'.  

Notuce that variable **time** is continuous and can not be utilized directly for inference.
Oftenly non-learning **rules-based** used, which has multiple problems in production: hard thresholds, doesn't scale, non-learnt rules.

```{r model-1, echo=FALSE}
model_1 <- '
var foreach = function(lst, fn) {
var foreach_ = function(i) {
if (i < lst.length) {
fn(lst[i]);
foreach_(i + 1);
}
};
foreach_(0);
};

var model = function() {

var conversionRates = {
"control":   uniform(0,1), 
"treatment": uniform(0,1),
};

foreach(data, function(personData) {

var acceptanceRate = conversionRates[personData.group] 

var converted_data = personData.converted == 1 ? true : false
observe(Bernoulli({p:acceptanceRate}), converted_data)

});

var ret = {
"control": conversionRates["control"], 
"treatment": conversionRates["treatment"], 
"delta": conversionRates["control"] - conversionRates["treatment"],
};

return ret
}
var numSamples1 = 20000;  
var inferOpts1 = { method: "MCMC",  samples: numSamples1, burn: numSamples1/2, verbose: true};

var numSamples2 =20000;  
var inferOpts2 = {
method: "incrementalMH", samples: numSamples2, burn: numSamples2/2,verbose: true, verboseLag: numSamples2/10}

Infer(inferOpts2, model);
'

p_model_1 = webppl(model_1, data = df_banner, data_var = "data")
p_model_1_countries = webppl(model_1, data = df_countries200, data_var = "data")
``` 

```{r model-2, echo=FALSE}
model_2 <- '
var foreach = function(lst, fn) {
    var foreach_ = function(i) {
        if (i < lst.length) {
        fn(lst[i]);
        foreach_(i + 1);
        }
    };
    foreach_(0);
};

var model = function() {

  // hypothesis for model1-no-Robot vs model2 with Human-Robot
  var hypothesis = flip(0.5); // initial guess for Model-1 

  // mixture parameter (i.e., percent of human vs robot visitors)
  var humanRobotBinomProb = uniform(0,1); 
  
  // mu-sigma of <logtime spent on the website> for groups convert vs treatment
  var mu = {
    "g1": uniform(0., 23.0),   
    "g2": uniform(0., 10.0),  
  }
  var sigmas =  {
    "g1": uniform(0.0, 12.0),  
    "g2": uniform(0.0, 12.0),  
  }
  
  // robots do not convert
  var conversionRatesM1 = {
    "control":   uniform(0,1), 
    "treatment": uniform(0,1),
  };

  // robots do not convert
  var conversionRates = {
    "control":   uniform(0,1), 
    "treatment": uniform(0,1),
    "robot": uniform(0,1),
  };

  foreach(data, function(personData,hypothesis) {

        // Human vs. Robot by hour spent on website
        // Robot visitors have a very DIFFERENT time and conversion probability 
        var human_robot_group = flip(humanRobotBinomProb) ? "g1" : "g2";
        
        var acceptanceRate =  
                hypothesis ? 
                conversionRatesM1[personData.group]: 
                (human_robot_group == "g1") ? conversionRates[personData.group] : conversionRates["robot"]

        // visitors are i.i.d.
        var hourPerson =  Gaussian({mu: mu[human_robot_group], sigma:sigmas[human_robot_group]})
        observe(hourPerson, personData.hour)
        
        var converted_data = personData.converted == "1" ? true : false
        observe(Bernoulli({p:acceptanceRate}), converted_data)
    
    });
    
    var hour_g1 = gaussian({mu: mu["g1"], sigma: sigmas["g1"]})
    var hour_g2 = gaussian({mu: mu["g2"], sigma: sigmas["g2"]})

  var ret = {
  "hypothesis": hypothesis,
  "controlM1": conversionRatesM1["control"], 
  "treatmentM1": conversionRatesM1["treatment"], 
  "humanRobotBinomProb": humanRobotBinomProb,
  "hour_human": hour_g1, 
  "hour_robot": hour_g2, 
  "robot": conversionRates["robot"], 
  "control": conversionRates["control"], 
  "treatment": conversionRates["treatment"], 
  "delta": conversionRates["control"] - conversionRates["treatment"],
  "delta_control_robot": conversionRates["control"] - conversionRates["robot"]
  };
  
  return ret
}
var numSamples1 = 1000; 
var inferOpts1 = { method: "MCMC",  samples: numSamples1, burn: numSamples1/2, verbose: true};

var numSamples2 =100000; // 100000;
var inferOpts2 = {
method: "incrementalMH", samples: numSamples2, burn: numSamples2/2,verbose: true, verboseLag: numSamples2/10}

Infer(inferOpts2, model);
'

p_model_2 = webppl(model_2, data = df_banner, data_var = "data")
p_model_2_countries = webppl(model_2, data = df_countries200, data_var = "data")
```


```{r save-all, echo=TRUE}
fname1 = "~/PycharmProjects/tests/webppl/Results2/models_banner_countries_snaphot_R.Rdata"
save.image(fname1)
fname2 = "~/PycharmProjects/tests/webppl/models_banner_countries_p1_p2.Rdata"
save(p_model_1, p_model_2, p_model_1_countries, p_model_2_countries, df_banner, df_countries200, file=fname2)
```


